Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-12-19 cover-letter/refactor-letter.tex
Revise the example and overview with reviewer comments

To aid in reviewing this new refactored manuscript, I am including here a detailed summary of the changes, and where possible, the submission itself indicates the changes directly to make it easier for the reviewers to inspect.
\begin{itemize}
  \item We rewrote the abstract to be active present tense, define the problem, approach, contributions, and results.
  \item We revised the introduction to pull in the last three paragraphs of section two, and to better funnel readers from the big picture, intuitive overview, to specific details on our tools and contributions. 
  \item We added a discussion section to the case study in section 8 to address lessons learned from our experience. We also enlarged significantly figures 14 and 17.
  \item We added a paragraph to the end of the example section explaining that our discussion of AGREE early in the paper, of necessity, is a birdseye view of its role in the BriefCASE workflow for the reader that perhaps doesn't want all the detail in the following sections. The actual AGREE section of the paper then presents notation, semantics, and usage so that the reader is able to contextualize our primary contributions. We also added in that paragraph direct references to the sections in the paper where the detailed contracts for the example system are discussed. 
\end{itemize}

>>>>

To aid in reviewing this new refactored manuscript, I am including here a detailed summary of the changes, and where possible, the submission itself indicates the changes directly to make it easier for the reviewers to inspect.
\begin{itemize}
  \item We rewrote the abstract to be active present tense, define the problem, approach, contributions, and results.
  \item We revised the introduction to pull in the last three paragraphs of section two, and to better funnel readers from the big picture, intuitive overview, to specific details on our tools and contributions. 
  \item We added a discussion section to the case study in section 8 to address lessons learned from our experience. We also enlarged significantly figures 14 and 17.
  \item We removed the overview section, created a new figure showing the workflow through the briefcase tool, and integrated that into the example section. We added to the example section references to the workflow figure. We moved to the beginning of the section a better overview of the example UAV system, and we added text explaining why the system must be cyber-resilient. We did not remove sections 3.1 - 3.3 as suggested by the reviewer as these sections discuss the paper contributions at a high-level in the context of our illustrative example. We did verify that we had appropriate references to the example, and its various figures, in those sections as suggested by the reviewer.
  \item We verified that sections 4 through 7 (now sections 3 through 6) have appropriate references to the example system.
  \item We added a paragraph to the end of the example section explaining that our discussion of AGREE early in the paper, of necessity, is a birdseye view of its role in the BriefCASE workflow for the reader that perhaps doesn't want all the detail in the following sections. The actual AGREE section of the paper then presents notation, semantics, and usage so that the reader is able to contextualize our primary contributions. We also added in that paragraph direct references to the sections in the paper where the detailed contracts for the example system are discussed. 
\end{itemize}

### 2022-12-19 paper/intro.tex
Revise the example and overview with reviewer comments

\newjunk{%
The contributions of this paper relate to the aspects of \brfcs\ concerning evidence that a high-assurance component meets its intended purpose and is properly implemented. 
%
We leverage the existing {\agr}\footnote{AGREE is the acronym for \emph{Assume Guarantee Reasoning Environment}.} model checker to provide evidence of the former and the existing verified \ckml\ compiler to provide evidence of the latter \cite{agree2013,cakeml}. 
%
Specifically, designers write \emph{contracts} to formally specify input and output properties of the system and its components, and \agr\ proves via model checking whether or not the system composition preserves contract requirements at component inputs and guarantees contract obligations at system outputs.
%
In this way, \agr\ provides the formal framework we use to describe the behavior of an inserted high-assurance component, such as a filter or monitor, and then prove if adding such a component to the system improves
cyber-resiliency.
}

@@

\newjunk{
As such, this paper defines a
\emph{code contract} language that is a subset of the \agr\ language
but with sequential evaluation semantics as opposed to \agr's existing
parallel semantics.  The sequential semantics are requisite to
code synthesis and are defined such that \agr\ is able to still prove the contract composition of the system works.
This paper further defines a notion of \emph{test contract} for unit
testing code contracts outside of the system composition to verify
input to output behavior as well as general properties of the code
contract.  
%
Intuitively, the behavior of a high assurance component is
defined by the designer in a code contract, the designer then writes test contracts to validate that behavior by asking \agr\ to prove if the code contract ensures the output obligations in the test contract under the test contracts input assumptions.
%
Once the designer is satisfied that the code
contract is correct, the system composition, with its various contracts, is verified to conclude
that the system meets its cyber-requirements.
}

>>>>

\newjunk{%
The contributions of this paper relate to the aspects of \brfcs\ concerning evidence that a high-assurance component meets its intended purpose and is properly implemented. 
%
We leverage the existing {\agr}\footnote{AGREE is the acronym for \emph{Assume Guarantee Reasoning Environment}.} model checker to provide evidence of the former and the existing verified \ckml\ compiler to provide evidence of the latter \cite{agree2013,compositional-analysis-agree,nfm:agree,cakeml}. 
%
Specifically, designers write \emph{contracts} to formally specify input and output properties of the system and its components, and \agr\ proves via model checking whether or not the system composition preserves contract requirements at component inputs and guarantees contract obligations at system outputs.
%
In this way, \agr\ provides the formal framework we use to describe the behavior of an inserted high-assurance component, such as a filter or monitor, and then prove if adding such a component to the system improves
cyber-resiliency.
}

@@

\newjunk{
As such, this paper defines a
\emph{code contract} language that is a subset of the \agr\ language
but with sequential evaluation semantics as opposed to \agr's existing
parallel semantics.  The sequential semantics are requisite to
code synthesis and are defined such that \agr\ is able to still prove the contract composition of the system works.
This paper further defines a notion of \emph{test contract} for unit
testing code contracts outside of the system composition to verify
input to output behavior as well as general properties of the code
contract.  
%
Intuitively, the behavior of a high assurance component is
defined by the designer in a code contract, the designer then writes test contracts to validate that behavior by asking \agr\ to prove if the code contract ensures the output obligations in the test contract under the test contract's input assumptions.
%
Once the designer is satisfied that the code
contract is correct, the system composition, with its various contracts, is verified to conclude
that the system meets its cyber-requirements.
}
